One Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
Updated article by addding lag analysis in appendix and footnote in text

```{=latex}
\keywords{ discourse analysis, presidential speeches, transnational governance, environmental policy, Brazilian Amazon, supervised learning}
```
```{=latex}
\wordcount{ 8190 (including abstract, text, references, and footnotes)}
```
```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(ggplot2)
library(plm)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

While we identified the effects of setting and urgency on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends. Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985.Interestingly, and to begin with, peak years identified in Figure 2 do not coincide with increases of specific problem-constructions in Figure 3.

@@

In terms of future research, we see at least three possibilities.First, scholars should investigate how problem-constructions change across settings and over time for other Amazonian countries or other policy objects, and in comparative ways. For example, recent literature demonstrates that reductions in deforestation in the Amazon lead to increased deforestation in the Cerrado biome[@villoria2022]. By comparing the Amazonian statements and Cerrado statements, we could identify to what extent other problems are ignored in favour of the "Amazon problem". Moreover, social media can change political communications in fundamental ways. The spread of political communications in social media could, on the one hand, contribute to diminishing the importance of physical settings and make presidents less likely to afford diverging problem-constructions. On the other hand, micro-targeting of social media algorithms could enhance how different problem-constructions are distributed to audiences. We look forward to works that investigate variation in problem-constructions in the era of social media. Finally, in a forthcoming article, Ajzenman, Cavalcanti, and Da Mata (2020) propose an identification strategy that ties Bolsonaro's speech to covid-19 infections. While we do not explicitly conceptualize how various problem-constructions might directly affect outcomes, we look forward to similar studies that identify how different problem-constructions affect (environmental) outcomes in more direct ways.

@@

>>>>

```{=latex}
\keywords{ discourse analysis, presidential speeches, transnational governance, environmental policy, Brazilian Amazon, supervised learning}
```
```{=latex}
\wordcount{ 8190 (including abstract, text, references, and footnotes)}
```
```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(ggplot2)
library(plm)
library(timetk)
library(lubridate)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

While we identified the effects of setting and urgency on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends. Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985. Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3 ^[4].

^[4]: We also run lag analysis to uncover hidden patterns and identify seasonality in our data. Autocorrelation and partial autocorrelation plots for the proportion of problem-constructions in time are displayed in the appendix. The plots illustrate no significant autocorrelations between peak years and problem-constructions.

@@

In terms of future research, we see at least three possibilities.First, scholars should investigate how problem-constructions change across settings and over time for other Amazonian countries or other policy objects, and in comparative ways. For example, recent literature demonstrates that reductions in deforestation in the Amazon lead to increased deforestation in the Cerrado biome [@villoria2022]. By comparing the Amazonian statements and Cerrado statements, we could identify to what extent other problems are ignored in favour of the "Amazon problem". Moreover, social media can change political communications in fundamental ways. The spread of political communications in social media could, on the one hand, contribute to diminishing the importance of physical settings and make presidents less likely to afford diverging problem-constructions. On the other hand, micro-targeting of social media algorithms could enhance how different problem-constructions are distributed to audiences. We look forward to works that investigate variation in problem-constructions in the era of social media. Finally, in a forthcoming article, Ajzenman, Cavalcanti, and Da Mata (2020) propose an identification strategy that ties Bolsonaro's speech to covid-19 infections. While we do not explicitly conceptualize how various problem-constructions might directly affect outcomes, we look forward to similar studies that identify how different problem-constructions affect (environmental) outcomes in more direct ways.

@@

```{r peak years test, fig.cap="Lag analysis for problem-constructions and for year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_mx %>%
  count(year, mx_cat) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n),
         year = lubridate::as_date(year)) %>% 
  select(-n) %>%
  filter(mx_cat != "Other") %>%
  group_by(mx_cat) %>% 
  plot_acf_diagnostics(.date_var = year,
                       .value = perc,
                       .show_white_noise_bars = TRUE,
                       .interactive = FALSE)
```
